Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-31 parts/sa.tex
fix allProcs
start cleanup

\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  The reachability of a process $a_j$ prof a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj = \{ \PHobj{a_i}{a_j} \mid a \in \PHs \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P \in \Obj$, where $P = \PHobj{a_i}{a_j}$, $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$.
  An objective $P$ is \emph{trivial} is $\PHtarget(P)=\PHbounce(P)$.
\end{definition}

@@

For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$, and
$ps \in \powerset(\Proc), ps \subseteq \ctx \Leftrightarrow \forall a_i \in ps, a_i \in \ctx$.
%The override of a context $\ctx$ by a set of processes $ps$ is noted $\ctx \Cap ps$ (\defref{ctxcap}).
%Par exemple, $\state{a_1,a_2,b_1,c_1}\Cap\{ a_3, b_2, b_3 \} = \state{a_3,b_2,b_3,c_1}$.
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \mapsto \Ctx$]
\label{def:ctxcap}
  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}

A scenario $\delta \in \Sce$ is \emph{playable} in a context $\ctx$ if and only if $\supp(\delta) \subseteq \ctx$. 
The play of $\delta$ in $\ctx$ is denoted $\ctx \PHplay \delta$ where $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$.

\begin{definition}[Objective sequence ($\OS$)]
\label{def:OS}
\towrite{Simplifier / réécrire en dehors d'une def}
  An \emph{objective sequence} is a sequence $\w = P_1 \concat \dots \concat P_{|\w|}$,
  where $\forall n \in \indexes{\w}, \w_n \in \Obj$ and $a_i = \PHtarget(\w_n) \Rightarrow \last_a(\w_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all objective sequences is denoted by $\OS$.
  The definitions of $\last_a$ \todo{À définir}, $\first_a$ \todo{À définir}, $\supp$ \todo{À définir} and $\ceil$ \todo{À définir}
  are simply derived by omitting the case of hitters.
\end{definition}

@@

\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
\label{def:concr}
\towrite{Simplifier ? Supprimer la def formelle ?}
  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
  \begin{align*}
    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
    \\ &
      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
    \\ &
      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
    \}
    \enspace,
  \end{align*}
  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
\end{definition}
%
\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:concr-set}
  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
\end{definition}

\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \uconcr(\w) = 
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \supp(\delta) \subseteq s \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{theorem}
\label{th:uconcr-ctx}
  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset \enspace.$
\end{theorem}
% 
\begin{definition}[$\uconcr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:uconcr-set}
  $\uconcr(\Omega) = \{ \delta \in \uconcr(\w) \mid \w \in \Omega\}$
\end{definition}

The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \} \\
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}

@@

@@

\begin{definition}[Coherent solution]
\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\myrsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\myreq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}

\begin{theorem}[Approximation inf.]
\label{th:approxinf}
  If the graph $\cwB$ contains no cycle,
  all objectives have at least one solution
  and all cooperative sort requisites are coherent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}

@@

\begin{itemize}
  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$,
    or $\forall \zeta \in \BS(P), \zeta \in \Sce \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$ and $\delta$ is given by \pref{th:autohits}.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};

>>>>

\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  The reachability of a process $a_j$ prof a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj = \{ \PHobj{a_i}{a_j} \mid a \in \PHs \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is \emph{trivial} if $a_i = a_j$.
\end{definition}
We define an \emph{objective sequence} as a sequence of objectives in which each target must be equal to the previous bounce of the same sort, if it exists.
The set of all objective sequences is denoted by $\OS$.

@@

For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\Proc) \cup \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
%The override of a context $\ctx$ by a set of processes $ps$ is noted $\ctx \Cap ps$ (\defref{ctxcap}).
%Par exemple, $\state{a_1,a_2,b_1,c_1}\Cap\{ a_3, b_2, b_3 \} = \state{a_3,b_2,b_3,c_1}$.

\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \mapsto \Ctx$]
\label{def:ctxcap}
  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}

A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
%$\supp(\delta) \subseteq \ctx$. 
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.

\begin{comment}
  \begin{definition}[Objective sequence ($\OS$)]
  \label{def:OS}
  \towrite{Simplifier / réécrire en dehors d'une def}
    An \emph{objective sequence} is a sequence $\w = P_1 \concat \dots \concat P_{|\w|}$,
    where $\forall n \in \indexes{\w}, \w_n \in \Obj$ and $a_i = \PHtarget(\w_n) \Rightarrow \last_a(\w_{1..n-1}) \in \{ \varnothing, a_i \}$.
    The set of all objective sequences is denoted by $\OS$.
    The definitions of $\last_a$ \todo{À définir}, $\first_a$ \todo{À définir}, $\supp$ \todo{À définir} and $\ceil$ \todo{À définir}
    are simply derived by omitting the case of hitters.
  \end{definition}
\end{comment}

@@

We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if it contains scenarios starting from all states $s \subseteq \ctx$.
if such a scenario exists in all states $s \subseteq \ctx$.

\begin{comment}
\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
\label{def:concr}
\towrite{Simplifier ? Supprimer la def formelle ?}
  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
  \begin{align*}
    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
    \\ &
      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
    \\ &
      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
    \}
    \enspace,
  \end{align*}
  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
\end{definition}
%
\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:concr-set}
  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
\end{definition}
\end{comment}

\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \uconcr(\w) = 
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{theorem}
\label{th:uconcr-ctx}
  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset$.
\end{theorem}

\begin{comment}
\begin{definition}[$\uconcr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:uconcr-set}
  $\uconcr(\Omega) = \{ \delta \in \uconcr(\w) \mid \w \in \Omega\}$
\end{definition}
\end{comment}

The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}

@@

\towrite{expliquer maxCont et le graphe de causalité}

@@

\begin{definition}[Coherent solution]
\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}

\begin{theorem}[Under-Approximation]
\label{th:approxinf}
  If the graph $\cwB$ contains no cycle,
  all objectives have at least one solution
  and all cooperative sort requisites are coherent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}

@@

\begin{itemize}
  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
    or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a sequence given by \pref{th:hcompcomp}.

@@

\begin{figure}[p]
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};
